Assignment 2

### 2019-06-28 ex2/report/report.tex
Changed report

In this document, we redo parts of a recent paper which bases on the CIC-IDS-2017 dataset for evaluating the performance of several feature vectors and machine learning techniques for accurate anomaly detection. We use explainability methods for investigating if the decisions the anomaly detectors untertake are reasonable.

@@

\section{Machine Learning Approaches for Traffic Classification}
\subsection{Deep Learning}
\subsection{Random Forests}

\section{Explainability Plots}
\subsection{Partial Dependence Plots}
Partial Dependence Plots (PDP) visualize dependence of a model's predictions by plotting the model's prediction for a modified dataset for which the feature's value has been fixed to a certain value and computing the an average over the dataset.

@@

In an attempt to overcome this problem, it is possible to only consider samples which are likely to occur for certain feature values, i.e. to consider the conditional distribution of remaining features, for computing explainability graphs. This is the concept for Accumulated Local Effects (ALE) plots.

@@

\section{Logistic Regression as Surrogate Model}

\section{Implementing a Backdoor}

@@

>>>>

In this document, we redo parts of a recent paper~\cite{fares} which bases on the CIC-IDS-2017 dataset for evaluating the performance of several feature vectors and machine learning techniques for accurate anomaly detection. We use explainability methods for investigating if the decisions the anomaly detectors untertake are reasonable.

@@

\section{Machine Learning Approaches for Anomaly Detection} \label{sec:ml_approaches}
\subsection{Deep Learning}
\subsection{Random Forests}

\subsection{Performance Results}
\section{Explainability Plots}
Several graphs have been proposed for visualizing feature dependence of non-interpretable machine learning models~\cite{goldstein2015peeking, friedman2001greedy, apley2016visualizing}.
In this section, we introduce the graphs which we will use for interpreting our models' outcomes. 
\subsection{Partial Dependence Plots}
Partial Dependence Plots (PDP) visualize dependence of a model's predictions by plotting the model's prediction for a modified dataset for which the feature's value has been fixed to a certain value and computing the an average over the dataset.

If we denote by $f^{i}$ the marginal distribution of the feature space which retains all features except the $i$th feature $x_i$, the PDP for $x_i$ feature can be expressed as
\begin{equation}
\text{PDP}_i(x) = \mathbb E_{\boldsymbol X}\left(Predict(X_1,\ldots,X_{i-1},x,X_{i+1},\ldots X_n)\right) % \int _{\mathbb R^n} Predict(x_1,\ldots,x_{i-1},x,x_{i+1},\ldots x_n) f(\boldsymbol x) d\boldsymbol x .
\end{equation}
Empirically, we can approximate the distribution of the feature space by the observed samples. Hence, at a given point $x$ the PDP can be found by setting the corresponding values of all samples in the dataset to $x$ and averaging over the predictions of the resulting modified dataset.

@@

In an attempt to overcome this problem, it is possible to only consider samples which are likely to occur for certain feature values, i.e. to consider the conditional distribution of remaining features, for computing explainability graphs. This results the concept for Accumulated Local Effects (ALE) plots.

For a feature $X_i$ the ALE plot ALE$_i(x)$ can be defined differentially as

\begin{equation}
\frac{d}{dx} \text{ALE}_i (x) = \mathbb E_{\boldsymbol X | X_i}\left(\frac{d}{d_x} Predict(X_1,\ldots,X_{i-1},x,X_{i+1},\ldots X_n) | X_i=x\right)
\end{equation}

To combat ambiguity of this definition, we force ALE$_i(x)$ to have zero mean on the domain of $X_i$.

For empirical evaluation, we approximate the conditional distributions of $\boldsymbol X$ by averaging over samples for which $X_i \approx x$.

@@

\section{Logistic Regression as Surrogate Model}
Another possibility for explaining the models' outcomes is training an interpretable surrogate model to the predictions that the original non-interpretable model makes. We trained a logistic regression classifier to the predictions our models made. Table~\ref{tab:logreg_results} shows the detection performance for logistic regression when training to labels our models predicted, and to the original lables, respectively. As expected, detection performance is considerably worse than for the more sophisticated models used in Section~\ref{sec:ml_approaches}. The fact that results for random forests are very similar to original data is due to the good detection performance of random forests. Hence, there is hardly any difference when training with the real labels and with the prediction of the random forest.

 Table~\ref{tab:logreg_coeff} displays the coefficients for 
\subsection{Interpretation}
\section{Implementing a Backdoor}

\section{Misclassification Examples}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}
